Toxic Code Snippets on Stack Overflow

### 2018-11-21 cloverflow-tse/cover_letter/second_round/cover_letter.tex
Incorporated Matheus's comments.

This paper is a journal-first submission to Transactions on Software Engineering. This is a minor revision of the submission no.~TSE-2018-06-0228 and we would like to thank the anonymous reviewers for taking their time to read our paper carefully. With their useful and constructive reviews, we improved the work further as listed below and as discussed later in this letter.

@@

We agree that our analysis may not fully answer your comment because we could not capture what Stack Overflow visitors actually do when they already expect an outdated answer. The most proper method for this may be doing another developer survey. However, our investigation tries to at least shade light on this by comparing the popularity of the outdated answer and the newer answers based on the number of votes. If Stack Overflow visitors reuse the code (or learn from the answers) and they like the answer, they can reward the answer with an upvote. In our investigation of the 100 outdated answers, we found that only 5 of the newer answers had higher votes than the outdated answers and 99\% of the outdated answers were still marked as accepted. We are aware that this may be affected by the duration that the answers appear on a Stack Overflow post. The newer answers have less visibility compared to the older answers.

@@

\section{Conclusion}
We would like to thank the reviewers again for their comments.
We have tried our best to address every concern that has been pointed out by the reviewers. This result in several minor improvements throughout the paper.

>>>>

This paper is a journal-first submission to Transactions on Software Engineering. This is a minor revision to the submission no.~TSE-2018-06-0228 and we would like to thank the anonymous reviewers for taking their time to read our paper carefully. With their useful and constructive reviews, we improved the work further as listed below and as discussed later in this letter.

@@

We agree that our analysis may not fully answer your comment because we could not capture what Stack Overflow visitors actually do when they already expect an outdated answer. The most proper method for this may be doing another developer survey. However, our investigation tries to shade light on this by comparing the popularity of the outdated answer and the newer answers based on the number of votes. If Stack Overflow visitors reuse the code (or learn from the answers) and they like the answer, they can reward the answer with an upvote. In our investigation of the 100 outdated answers, we found that only 5 of the newer answers had higher votes than the outdated answers and 99\% of the outdated answers were still marked as accepted. We are aware that this may be affected by the duration that the answers appear on a Stack Overflow post. The newer answers have less visibility compared to the older answers.

@@

\section{Conclusion}
We would like to thank the reviewers again for their comments.
We have tried our best to address every concern that has been pointed out by the reviewers. This result in several improvements throughout the paper.
